Quantifying maternal reproductive output of chondrichthyan fishes

### 2024-06-23 reports/figs.tex
repo_prep

\includegraphics[width=1\linewidth]{figure1.png}

@@

\includegraphics{unnamed-chunk-2-1.pdf}

@@

\includegraphics{unnamed-chunk-3-1.pdf}

@@

\includegraphics{unnamed-chunk-4-1.pdf}

@@

\includegraphics{unnamed-chunk-5-1.pdf}

@@

\includegraphics{unnamed-chunk-6-1.pdf}

@@

\includegraphics{unnamed-chunk-7-1.pdf}

>>>>

\includegraphics[width=1\linewidth]{../img/figure1}

@@

\includegraphics{/Users/avh/Library/CloudStorage/OneDrive-DepartmentofPrimaryIndustriesAndRegionalDevelopment/manuscripts/maternity-function/reports/figs_files/figure-latex/unnamed-chunk-2-1.pdf}

@@

\includegraphics{/Users/avh/Library/CloudStorage/OneDrive-DepartmentofPrimaryIndustriesAndRegionalDevelopment/manuscripts/maternity-function/reports/figs_files/figure-latex/unnamed-chunk-3-1.pdf}

@@

\includegraphics{/Users/avh/Library/CloudStorage/OneDrive-DepartmentofPrimaryIndustriesAndRegionalDevelopment/manuscripts/maternity-function/reports/figs_files/figure-latex/unnamed-chunk-4-1.pdf}

@@

\includegraphics{/Users/avh/Library/CloudStorage/OneDrive-DepartmentofPrimaryIndustriesAndRegionalDevelopment/manuscripts/maternity-function/reports/figs_files/figure-latex/unnamed-chunk-5-1.pdf}

@@

\includegraphics{/Users/avh/Library/CloudStorage/OneDrive-DepartmentofPrimaryIndustriesAndRegionalDevelopment/manuscripts/maternity-function/reports/figs_files/figure-latex/unnamed-chunk-6-1.pdf}

@@

\includegraphics{/Users/avh/Library/CloudStorage/OneDrive-DepartmentofPrimaryIndustriesAndRegionalDevelopment/manuscripts/maternity-function/reports/figs_files/figure-latex/unnamed-chunk-7-1.pdf}
